Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO

### 2016-04-07 Paper/paper.tex
updated methods & other secs

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Techniques}\label{s1:techniques}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Waveform Models}\label{s2:waveforms}

@@

The joint inferred probability distribution of all parameters 
$\vec{\Theta}:=\vec{\theta}\cup\{\lambdans\}$ 
is given by
\begin{equation}
 p(\vec{\Theta} | d_n, K) = \dfrac{p(d_n|\vec{\Theta}, K)\,p(\vec{\Theta} | K)}{p(d_n|K)}.
\end{equation}
Here, $p(\vec{\Theta} | K)$ is the prior probability for binary parameters of taking 
particular values. In this paper, we use a uniform prior on the individual masses within 
pre-chosen ranges, as well as a uniform prior on the spin of the black hole. We set neutron star's
spin identically $=0$, and its tidal deformability parameter $\lambdans$ to be equally likely
between $[0, 4000]$. The prior probability of obtaining a particular realization of data
$p(d_n|K)$ is absorbed into the overall normalization. Finally, the first term in the numerator
$p(d_n|\vec{\theta}, \lambdans, K)$ is the likelihood of obtaining the given stretch of 
data $d_n$ if we assume that a signal parameterized by $\vec{\theta}\cup\{\lambdans\}$ is buried
in it, i.e.
\begin{equation}\label{eq:likelihood}
 \LL(\vec{\Theta}) \equiv p(\vec{\Theta} | K) = \mathcal{N} \mathrm{exp}[- \langle d_n - h | d_n - h\rangle ],
\end{equation}
where $h\equiv h(\vec{\Theta})$ is given by our waveform model LEA+, and the
detector noise weighted inner-product $\langle a|b\rangle$ is defined as 
$$
\langle a|b\rangle \equiv 4\,\mathrm{Re}\left[\int_0^\infty \dfrac{\tilde{a}(f) \tilde(b)(f)^*}{S_n(|f|)}\,\D f\right],
$$
where $\tilde{a}$ means the Fourier transform of the finite time series $a(t)$, and 
$S_n(|f|)$ is the one-sided amplitude spectrum of detector noise. The definition of $\LL$ in 
Eq.~\ref{eq:likelihood} assumes that the instrument noise is colored Gaussian.

@@

\includegraphics[trim={3cm 0 0 0},width=2.3\columnwidth]{plots/TTLambdaCIWidths90_0_Lambda_SNR.pdf}

@@

\includegraphics[width=1.025\columnwidth]{plots/TTSNRThresholdFor200LambdaMeasurement_BHspin_BHmass_Lambda1000_0_CI90_0}
\includegraphics[width=1.025\columnwidth]{plots/TTSNRThresholdFor100LambdaMeasurement_BHspin_BHmass_Lambda1500_0_CI90_0}

@@

\includegraphics[width=1.025\columnwidth]{plots/TTLambdaErrorCurves_BHspin_BHmass_SNR20_CI90_0.pdf}
\includegraphics[width=1.025\columnwidth]{plots/TTLambdaErrorCurves_BHspin_BHmass_SNR30_CI90_0.pdf}

@@

@@

In the previous section we showed that we begin to care for the effects of NS's
deformation due to its companion hole's tidal field, if (a) the BH is sufficiently
small, (b) BH spin is aligned and $\gtrsim +0.4$, and (c) the NS is
not very compact, with $\lambdans\gtrsim 1000$. The first two conditions
enhance tidal effects on emitted GWs by increasing the number of orbits at small
separation, where the deviation of NSBH and BHBH dynamics is the largest. The third,
i.e. (c), simply makes the NS more easily deformable. All of them reduce the onset 
frequency for NS's disruption close to merger. Therefore, systems that fulfil the 
above conditions have considerably (or, at least, the most) different GW morphology
when compared to equivalent BHBH coalescences. Ultimately, the extent of 
tidal modulations of emitted GWs depends on the equation of state of neutron star
matter, which becomes an indirect measurable in GW astrophysics.
However, if we do indeed receive GWs from such a binary source, what information can we
possibly extract from it about the internal structure of neutron stars?
In this section we consider this question in perspective of measuring the tidal 
deformability parameter of neutron stars purely from gravitational waves they emits 
while orbiting spinning black holes.
We find that when the BH is sufficiently spinning in the prograde sense,
with $\chibh\gtrsim +0.7$, even at a relatively possible signal strengths ($\rho=20$),
we can begin to constraint $\lambdans$ at the level of $\pm 75\%$ errors with a $90\%$
confidence level. If the signal is stronger, say $\rho=30$, we can contraint
$\lambdans$ better with only $\pm 50\%$ errors, for binaries with large BH spins.
This trend continues as we vary the SNR from $\rho=30-50$ upwards. In other words,
with a single but moderately loud NSBH signal observation, Advanced LIGO will begin
to put constraints on NS matter properties. These constraints can consequently
be used to assess the likelihood of different equations of state for nuclear
matter, and possibly narrow the range they span.

@@

\includegraphics[width=1.025\columnwidth]{plots/RelErrorLambdaMedian_vs_N.pdf}
\includegraphics[width=1.025\columnwidth]{plots/LambdaCIWidths_vs_N.pdf}

@@

% 
\begin{figure}
\centering    
\includegraphics[width=\columnwidth]{plots/PowerLawCoefficient_LambdaErrorvsN_vs_Lambda.pdf}
\caption{This figure shows the relative uncertainty in the measurement of $\lambdans$,
as a function of $\lambdans$ itself. The drawn curves are cumulative, in the sense 
that the $N=n$ curve includes information from all of the first $n$ observed events.
Those corresponding to the first $N\leq 5$ events are shown in fading shades of red,
with the ones for higher value of $N$ being shown in grey (going from light to dark in
proportion to $N$).
Green dash-dotted lines are contours of $y=x^{-(1+1/5)}$.
% 
\prayush{We note that the measurement uncertainty from a population follows the
equation for the green lines.}
% 
}
\label{fig:TT_PowerLawLambdaErrorVsN}
\end{figure}
%

% 
\begin{figure*}
\centering    
\includegraphics[width=\columnwidth]{plots/LambdalErrorBars_vs_Lambda_N79_Log.pdf}
\includegraphics[width=\columnwidth]{plots/PowerLawCoefficient_LambdaErrorvsLambda_vs_N.pdf}
\caption{This figure shows the relative uncertainty in the measurement of $\lambdans$,
as a function of $\lambdans$ itself. The drawn curves are cumulative, in the sense 
that the $N=n$ curve includes information from all of the first $n$ observed events.
Those corresponding to the first $N\leq 5$ events are shown in fading shades of red,
with the ones for higher value of $N$ being shown in grey (going from light to dark in
proportion to $N$).
Green dash-dotted lines are contours of $y=x^{-(1+1/5)}$.
% 
\prayush{We note that the measurement uncertainty from a population follows the
equation for the green lines.}
% 
}
\label{fig:TT_Lambda_vs_Lambda_L500_2000_CI90_0_AllInOne}
\end{figure*}
%
% 
\textbf{Multiple identical sources at low SNR: }\label{s2:identical_multiple}
% 
% 
First we show a crude calculation which tells us that approximately $8$ (or $16$) 
observations
of NSBH signals with $\rho\geq 10$ distributed uniformly in effective volume, would
give us similarly accurate a measurement of $\lambdans$ as would a single detection
with $\rho=50$ (or $\rho=70$).

@@

\textbf{Astrophysical source population: }\label{s2:astro_multiple}
% 
Imagine we have $N$ stretches of data,
$d_1, d_2, \cdots, d_N$, each containing a single observation of an NSBH binary. Let $K$
denote our collective prior knowledge, except for expectations on binary parameters
themselves, which will enter the following calculation explicitly. Let the gravitational wave
signal from each binary be characterized by the parameters 
$\vec{\theta} = \{\mbh, \mns, \chibh, \chins, \rho\}$ and $\lambdans$. Note that we have folded
in the luminosity distance, inclination angle of the binary's orbital angular momentum with
respect to the plane of the detector, and its sky location angles into a single parameter $\rho$,
which is the SNR of the received signal. Note also that $\vec{\theta}$ does not include
$\lambdans$ as the latter would be treated independently. In addition we assume that all
NS's in a population will have the same deformability parameter $\lambdans$, and therefore
its cumulative measurement is possible.
% 
Using Bayes' theorem, the measured probability distribution function for $\lambdans$
from $N$ observations is
\begin{equation}\label{eq:lambdaMultiple}
 p(\lambdans | d_1, d_2, \cdots, d_N; K) = p(\lambdans | K)^{1-N}\prod_{i=1}^N p(\lambdans | d_i, K),
\end{equation}
where $p(\lambdans|K)$ is the prior expectation for $\lambdans$, and we have assumed
that all of the $N$ observations are independent. A priori, we assume that no 
particular value of $\lambdans$ is more preferred over another, and $\lambdans\leq 4000$,
i.e.
\begin{equation}\label{eq:lprior}
 p(\lambdans | K) = \dfrac{1}{4000}\,\mathrm{Rect}\left(\frac{\lambdans-2000}{4000}\right)
\end{equation}
% 
The second set of terms in Eq.~\ref{eq:lambdaMultiple} of the form $p(\lambdans | d_i, K)$
is each the probability distribution for $\lambdans$ inferred {\it a posteriori} from
the \textit{i}-th observation independently. 
They are calculated by integrating
\begin{equation}
 p(\lambdans | d_i, K) = \int \D \vec{\theta}\, p(\vec{\theta}, \lambdans | d_i, K),
\end{equation}
where $p(\vec{\theta}, \lambdans | d_n, K)$ is the inferred joint probability 
distribution of all source parameters $\vec{\theta}\cup\{\lambdans\}$ for the 
$i$-th event, as described in Sec.~\ref{s2:bayesian}.

>>>>

Next, we study the ability of aLIGO to constrain neutron star tidal 
deformability with a single observation of coalescing NSBHs. For this, we
use the same setup and parameter choices for signal waveforms as before, but
replace the template model with one that includes tidal effects from inspiral
through to merger~\cite{Lackey:2013axa} (i.e. LEA+). First of all, this reduces
the biases in the measurement of non-tidal parameters. Second, as we can see
from Fig.~\ref{fig:TT_LambdaCIWidths90_0_Lambda_SNR}, at signal-to-noise
ratios $\simeq 20-30$, only under the most favorable circumstance (including a
BH with mass within the ``mass-gap'') can we put a factor of $1.5-2$ bound on
$\lambdans$ at $90\%$ confidence level. For similar signals with 
$\rho\gtrsim 30$ we can constrain $\lambdans$ within $\pm 50\%$ of its true
value. For more realistic SNRs and BH parameters, a single measurement is 
for $\lambdans$ is accompanied with a $\sim\pm150+\%$. uncertainty. While these
results are expected, multiple realistic observations is the next window that 
we explore in order to obtain more information on $\lambdans$. These results 
are detailed in Sec.~\ref{s1:PEwithNS}.

Multiple realistic observations deliver far more information than what a single
observation furnishes, as has been shown the case to be for binary neutron
stars~\cite{DelPozzo:13}. As our final study, we perform a fully-Bayesian 
analysis of how our estimation of $\lambdans$ changes as we accumulate more and
more detections. The choices that determine the population are important here,
and were made as follows. Neutron star mass is fixed for signals at
$1.35M_\odot$, and its spin $\chins=0$. Black hole mass is sampled uniformly
from the range $[2,5]\times 1.35=[2.7, 6.75]M_\odot$. Our choice here is given
by the intersection set of the mass range that allows for neutron star disruption
and the range supported by the waveform model LEA+~\cite{Foucart2012,
Foucart:2013a,Lackey:2013axa}. Black hole spin is sampled uniformly from the
{\it aligned} range, i.e. $\chibh\in[0,+1]$. The true deformability is fixed
once per population, sampled uniformly from the range $\lambdans\in[0,2000]$.
In order to keep the computational cost tractable, we make a further 
approximation. We inject signals into zero noise at different SNRs and recover
their parameters from Bayesian inferencing for a fixed set of binaries,
whose parameters lie on a uniform grid given by:
$q=\{2,3,4,5\}\times\chibh=\{-0.5,0,0.5,0.75\}\times\lambdans=\{500,800,1000,1500,2000\}\times\rho=\{10,20,30,50,70\}$.
Once the population parameters been selected, each event's parameters are
replaced by their nearest neighbor in the above set. We make sure that this 
approximation is conservative by keeping our population sampling ranges within the
conservative side of the range spanned by the above set. With the caveats
laid out, we report our results in Sec.~\ref{s1:multiple_observations}.
% 
We find \prayush{[...]}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Techniques}\label{s1:techniques}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this section we summarize various technical aspects of this paper. The model
used to obtain tidal waveforms is described in Sec.~\ref{s2:waveforms}. The 
process of inferring source parameters from a GW signal is summarized in 
Sec.~\ref{s2:bayesian}. The process of generating and combining multiple events
is instead detailed in the corresponding results section,
Sec.~\ref{s2:astro_multiple}.

\subsection{Waveform Models}\label{s2:waveforms}

@@

We perform Bayesian parameter estimation for tidal signals, using
both tidal and non-tidal templates. The signal parameters are selected 
to lie on a grid given by:
$q=\{2,3,4,5\}\times\chibh=\{-0.5,0,0.5,0.75\}\times\lambdans=\{500,800,1000,1500,2000\}\times\rho=\{10,20,30,50,70\}$.
Corresponding signal waveforms are generated using the model described in the 
previous sub-section, and each injected into a separate zero noise data segment
$d_n$. Templates can be either tidal or non-tidal (LEA+ with $\lambdans=0$).

Inferred from $d_n$, the joint probability distribution for binary parameters
$\vec{\Theta}:=\vec{\theta}\cup\{\lambdans\}$ is given by
\begin{equation}\label{eq:postprob}
 p(\vec{\Theta} | d_n, K) = \dfrac{p(d_n|\vec{\Theta}, K)\,p(\vec{\Theta} | K)}{p(d_n|K)}.
\end{equation}
Here, $p(\vec{\Theta} | K)$ is the prior probability for binary parameters of
taking particular values. In this paper, we use a uniform prior on the
individual masses within pre-chosen ranges, as well as a uniform prior on the
spin of the black hole. We set neutron star's spin $=0$, and its tidal
deformability parameter $\lambdans$ is sampled uniformly from $[0, 4000]$. In
addition, we exclude mass-ratios between $[1,2]$ from our prior. This is done
because of model constraints for LEA+. The prior probability of obtaining a 
particular realization of data $p(d_n|K)$ is absorbed into the overall 
normalization. Finally, the first term in the numerator
$p(d_n|\vec{\theta}, \lambdans, K)$ is the likelihood of obtaining the given
stretch of data $d_n$ if we assume that a signal parameterized by
$\vec{\theta}\cup\{\lambdans\}$ is buried in it, i.e.
\begin{equation}\label{eq:likelihood}
 \LL(\vec{\Theta}) \equiv p(d_n| \vec{\Theta}, K) = \mathcal{N} \mathrm{exp}[- \langle d_n - h | d_n - h\rangle ],
\end{equation}
where $h\equiv h(\vec{\Theta})$ is a template given by our waveform model LEA+,
and the detector noise weighted inner-product $\langle a|b\rangle$ is defined 
as
\begin{equation}
\langle a|b\rangle \equiv 4\,\mathrm{Re}\left[\int_0^\infty \dfrac{\tilde{a}(f) \tilde(b)(f)^*}{S_n(|f|)}\,\D f\right],
\end{equation}
% 
where $\tilde{a}(f)$ is the Fourier transform of the finite time series $a(t)$,
and $S_n(|f|)$ is the one-sided amplitude spectrum of detector noise. The 
definition of $\LL$ in Eq.~\ref{eq:likelihood} assumes that the instrument
noise is colored Gaussian.

We sample the probability distribution given in Eq.~\ref{eq:postprob} using
an ensemble sampler Markov-chain Monte-Carlo algorithm based on the {\tt emcee}
package~. A total of $100$ independent walkers were used, each of which
was allowed to collect $100,000$ samples. We measure the correlation time and keep
only $20,000$ independent posterior points to further analyze the calculated 
posterior probability distributions. One simplifying assumption made to mitigate 
computational cost was setting the frequency sampling rate $\Delta f=0.4$~Hz, which
we found to be sufficient to calculate likelihoods robustly~\cite{Purrer:2015nkh}.
\prayush{TODO: MICHAEL}.

@@

\includegraphics[trim={3cm 0 0 0},width=2.\columnwidth]{plots/TTLambdaCIWidths90_0_Lambda_SNR.pdf}

@@

\includegraphics[width=0.9025\columnwidth]{plots/TTSNRThresholdFor200LambdaMeasurement_BHspin_BHmass_Lambda1000_0_CI90_0}
\includegraphics[width=0.9025\columnwidth]{plots/TTSNRThresholdFor100LambdaMeasurement_BHspin_BHmass_Lambda1500_0_CI90_0}

@@

\includegraphics[width=0.9025\columnwidth]{plots/TTLambdaErrorCurves_BHspin_BHmass_SNR20_CI90_0}
\includegraphics[width=0.9025\columnwidth]{plots/TTLambdaErrorCurves_BHspin_BHmass_SNR30_CI90_0}
\caption{In these figures we highlight the regions of BH mass and spin plane 
where we can constrain the $\lambdans$ of its companion NS within a factor of 
$1-2$ of its true value. Panels correspond to different signal strength, with 
$\rho$ increasing from left to right. Within each panel, $\lambdans$ 
measurement uncertainty contours are shown as functions of BH mass and spin,
with line-types corresponding to different uncertainty levels, and colors 
showing the injected $\lambdans$. 

@@

As hinted at in Fig.~\ref{fig:TT_LambdaCIWidths90_0_Lambda_SNR}, the 
measurability of NS tidal deformability improves with all factors that 
enhances the signature of the NS's disruption on the \textit{detectable} 
portion of the emitted GW signal (implying, within a frequency band set by the
detectors).

@@

In the previous section we showed that we begin to care for the effects of NS's
deformation due to its companion hole's tidal field, if (a) the BH is sufficiently
small, (b) BH spin is aligned and $\gtrsim +0.4$, and (c) the NS is
not very compact, with $\lambdans\gtrsim 1000$. The first two conditions
enhance tidal effects on emitted GWs by increasing the number of orbits at small
separation, where the deviation of NSBH and BHBH dynamics is the largest. The third,
i.e. (c), simply makes the NS more easily deformable. All of them reduce the onset 
frequency for NS's disruption close to merger. Therefore, systems that fulfil the 
above conditions have considerably (or, at least, the most) different GW morphology
when compared to equivalent BHBH coalescences. Ultimately, the extent of 
tidal modulations of emitted GWs depends on the equation of state of neutron star
matter, which becomes an indirect measurable in GW astrophysics.
% 
However, if we do indeed receive GWs from such a binary source, what information can we
possibly extract from it about the internal structure of neutron stars?
In this section we consider this question in perspective of measuring the tidal 
deformability parameter of neutron stars purely from gravitational waves they emits 
while orbiting spinning black holes.
% 
We find that when the BH is sufficiently spinning in the prograde sense,
with $\chibh\gtrsim +0.7$, even at a relatively possible signal strengths ($\rho=20$),
we can begin to constraint $\lambdans$ at the level of $\pm 75\%$ errors with a $90\%$
confidence level. If the signal is stronger, say $\rho=30$, we can contraint
$\lambdans$ better with only $\pm 50\%$ errors, for binaries with large BH spins.
This trend continues as we vary the SNR from $\rho=30-50$ upwards. In other words,
with a single but moderately loud NSBH signal observation, Advanced LIGO will begin
to put constraints on NS matter properties. These constraints can consequently
be used to assess the likelihood of different equations of state for nuclear
matter, and possibly narrow the range they span.

@@

\includegraphics[width=1\columnwidth]{plots/RelErrorLambdaMedian_vs_N.pdf}
\includegraphics[width=1\columnwidth]{plots/LambdaCIWidths_vs_N.pdf}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{plots/PowerLawCoefficient_LambdaErrorvsN_vs_Lambda.pdf}
\caption{This figure shows the relative uncertainty in the measurement of $\lambdans$,
as a function of $\lambdans$ itself. The drawn curves are cumulative, in the sense 
that the $N=n$ curve includes information from all of the first $n$ observed events.
Those corresponding to the first $N\leq 5$ events are shown in fading shades of red,
with the ones for higher value of $N$ being shown in grey (going from light to dark in
proportion to $N$).
Green dash-dotted lines are contours of $y=x^{-(1+1/5)}$.
\prayush{We note that the measurement uncertainty from a population follows the
equation for the green lines.}
\label{fig:TT_PowerLawLambdaErrorVsN}
\end{figure}
\includegraphics[width=\columnwidth]{plots/LambdalErrorBars_vs_Lambda_N79_Log.pdf}
\includegraphics[width=\columnwidth]{plots/PowerLawCoefficient_LambdaErrorvsLambda_vs_N.pdf}
\caption{This figure shows the relative uncertainty in the measurement of $\lambdans$,
as a function of $\lambdans$ itself. The drawn curves are cumulative, in the sense 
that the $N=n$ curve includes information from all of the first $n$ observed events.
Those corresponding to the first $N\leq 5$ events are shown in fading shades of red,
with the ones for higher value of $N$ being shown in grey (going from light to dark in
proportion to $N$).
Green dash-dotted lines are contours of $y=x^{-(1+1/5)}$.
\prayush{We note that the measurement uncertainty from a population follows the
equation for the green lines.}
\label{fig:TT_Lambda_vs_Lambda_L500_2000_CI90_0_AllInOne}

\textbf{Multiple identical sources at low SNR: }\label{s2:identical_multiple}
% 
First we show a crude calculation which tells us that approximately $8$ (or $16$) 
observations
of NSBH signals with $\rho\geq 10$ distributed uniformly in effective volume, would
give us similarly accurate a measurement of $\lambdans$ as would a single detection
with $\rho=50$ (or $\rho=70$).

@@

\textbf{Astrophysical source population: }\label{s2:astro_multiple}
% 
Imagine we have $N$ stretches of data,
$d_1, d_2, \cdots, d_N$, each containing a single observation of an NSBH binary. Let $K$
denote our collective prior knowledge, except for expectations on binary parameters
themselves, which will enter the following calculation explicitly. Let the gravitational wave
signal from each binary be characterized by the parameters 
$\,\vec{\theta} = \{\mbh, \mns, \chibh, \chins, \rho\}$ and $\lambdans$. Note that we have folded
in the luminosity distance, inclination angle of the binary's orbital angular momentum with
respect to the plane of the detector, and its sky location angles into a single parameter $\rho$,
which is the SNR of the received signal. Note also that $\vec{\theta}$ does not include
$\lambdans$ as the latter would be treated independently. In addition we assume that all
NS's in a population will have the same deformability parameter $\lambdans$, and therefore
its cumulative measurement is possible.
% 
Using Bayes' theorem, the measured probability distribution function for $\lambdans$
from $N$ observations is
\begin{equation}\label{eq:lambdaMultiple}
 p(\lambdans | d_1, d_2, \cdots, d_N; K) = p(\lambdans | K)^{1-N}\prod_{i=1}^N p(\lambdans | d_i, K),
\end{equation}
where $p(\lambdans|K)$ is the prior expectation for $\lambdans$, and we have assumed
that all of the $N$ observations are independent. A priori, we assume that no 
particular value of $\lambdans$ is more preferred over another, and $\lambdans\leq 4000$,
i.e.
\begin{equation}\label{eq:lprior}
 p(\lambdans | K) = \dfrac{1}{4000}\,\mathrm{Rect}\left(\frac{\lambdans-2000}{4000}\right)
\end{equation}
% 
The second set of terms in Eq.~\ref{eq:lambdaMultiple} of the form $p(\lambdans | d_i, K)$
is each the probability distribution for $\lambdans$ inferred {\it a posteriori} from
the \textit{i}-th observation independently. 
They are calculated by integrating
\begin{equation}
 p(\lambdans | d_i, K) = \int \D \vec{\theta}\, p(\vec{\theta}, \lambdans | d_i, K),
\end{equation}
where $p(\vec{\theta}, \lambdans | d_n, K)$ is the inferred joint probability 
distribution of all source parameters $\vec{\theta}\cup\{\lambdans\}$ for the 
$i$-th event, as described in Sec.~\ref{s2:bayesian}.
